\huge{ \emph{Supplement to} Algorithms For Shaping a Particle Swarm\\ With a Shared Control Input Using Boundary Interaction}

### 2016-09-02 RA-L/theory.tex
Replaced Shiva's files and changes images for pink borders

\begin{align}
F_{\text{\emph{forward}}} &=  F \sin(\theta) - F_f  \nonumber \\
\text{where }  F_f &= \begin{cases}  \mu_f N, &  \mu_f N < F \sin(\theta)  \label{eq:frictionmodel}  \\
F \sin(\theta), & \text{else} \end{cases} \\ %\sign(F \sin(\theta) ) \cdot  \max(0, | F sin\theta |- |F_f|)
\text{and } N &= F \cos(\theta) \nonumber
\end{align}
 Fig.~\ref{fig:friction} shows the resultant forces on two robots when one is touching a wall. As illustrated, both experiences different net forces although each receives the same inputs.
  For ease of analysis, the following algorithms assume $\mu_f$ is infinite and robots touching the wall are prevented from sliding along the wall.
This means that if one robot is touching the wall and another robot is free, if the control input is parallel or into the wall, the touching robot will not move. 
The next section shows how a system with friction model \eqref{eq:frictionmodel} and two orthogonal walls are sufficient to arbitrarily position two robots. 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\columnwidth]{friction.pdf} 
\vspace{-1em}
\caption{Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a robot near a wall, but not for a free robot.}
\label{fig:friction}
\end{center}
\end{figure}

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of $2$ Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{\begin{overpic}[width =\figwid]{one_1.jpg}\put(45,75){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_2.jpg}\put(45,75){$t$ = 0.25 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_3.jpg}\put(45,75){$t$  = 0.5 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_4.jpg}\put(45,75){$t$  = 0.75 s}
\end{overpic}
\begin{overpic}[width =\figwid]{one_5.jpg}\put(45,75){$t$  = 1 s}
\end{overpic}}\\
%{\begin{overpic}[width =\figwid]{two_1.jpg}\put(45,75){$t$  = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_2.jpg}\put(45,75){$t$  = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}\\
\vspace{.5em}
{\begin{overpic}[width =\figwid]{S3_1.jpg}\put(45,75){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_2.jpg}\put(45,75){$t$ = 0.25 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_3.jpg}\put(45,75){$t$  = 0.5 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_4.jpg}\put(45,75){$t$  = 0.75 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S3_5.jpg}\put(45,75){$t$  = 1 s}
\end{overpic}}
\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. The algorithm only requires friction along the bottom and left walls.
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  The path given by  Alg.\ \ref{alg:PosControl2Robots} is shown with solid arrows.
The bottom row shows an extreme case where the robots must switch position.
}
%\vspace{-2em}
}
\end{figure*}

>>>>

\begin{align}
F_{\text{\emph{forward}}} &=  F \sin(\theta) - F_f  \nonumber \\
\text{where }  F_f &= \begin{cases}  \mu_f N, &  \mu_f N < F \sin(\theta)  \label{eq:frictionmodel}  \\
F \sin(\theta), & \text{else} \end{cases} \\ %\sign(F \sin(\theta) ) \cdot  \max(0, | F sin\theta |- |F_f|)
\text{and } N &= F \cos(\theta) \nonumber
\end{align}
 Fig.~\ref{fig:friction} shows the resultant forces on two robots when one is touching a wall. As illustrated, both experiences different net forces although each receives the same inputs.
  For ease of analysis, the following algorithms assume $\mu_f$ is infinite and robots touching the wall are prevented from sliding along the wall.
This means that if one robot is touching the wall and another robot is free, if the control input is parallel or into the wall, the touching robot will not move. 
The next section shows how a system with friction model \eqref{eq:frictionmodel} and two orthogonal walls are sufficient to arbitrarily position two robots. 
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.8\columnwidth]{friction.pdf} 
\vspace{-1em}
\caption{Wall friction reduces the force for going forward $F_{\text{\emph{forward}}}$ on a robot near a wall, but not for a free robot. At left there is a fluid and inside it the velocity of the robot is almost zero at the surface and is more and more until it is the same as the free space on the threshold.}
\label{fig:friction}
\end{center}
\end{figure}

\section{Algorithms}\label{sec:algorithms}
\subsection{Position Control of $2$ Robots Using Wall Friction}\label{sec:PostionControl2Robots}
\begin{figure*}
\centering
\renewcommand{\figwid}{0.4\columnwidth}
{\begin{overpic}[width =\figwid]{S1_1.png}\put(55,15){$t$ = 0 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_2.png}\put(55,15){$t$ = 0.14 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_3.png}\put(55,15){$t$  = 0.29 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_4.png}\put(55,15){$t$  = 0.45 s}
\end{overpic}
\begin{overpic}[width =\figwid]{S1_5.png}\put(55,15){$t$  = 0.7 s}
\end{overpic}}\\
%{\begin{overpic}[width =\figwid]{two_1.jpg}\put(45,75){$t$  = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_2.jpg}\put(45,75){$t$  = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{two_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}\\
%\vspace{.5em}
%{\begin{overpic}[width =\figwid]{S3_1.jpg}\put(45,75){$t$ = 0 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_2.jpg}\put(45,75){$t$ = 0.25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_3.jpg}\put(45,75){$t$  = 0.5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_4.jpg}\put(45,75){$t$  = 0.75 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{S3_5.jpg}\put(45,75){$t$  = 1 s}
%\end{overpic}}
%\vspace{-1em}
\caption{\label{fig:shapeControlMathematica1}{Frames from an implementation of Alg.\ \ref{alg:PosControl2Robots}: two robot positioning using walls with infinite friction. The algorithm only requires friction along the bottom and left walls.
Robot initial positions are shown by a crosshair, and final positions by a circled crosshair.  Dashed lines show the shortest route if robots could be controlled independently.  The path given by  Alg.\ \ref{alg:PosControl2Robots} is shown with solid arrows.
%The bottom row shows an extreme case where the robots must switch position.
}
%\vspace{-2em}
}
\end{figure*}
